Reproducibility of COVID-19 pre-prints in 2020

### 2021-05-25 outputs/paper/paper.Rmd
Expand time frame of data collection, updates to cleaning scripts/files structure

---
title: "Reproducibility of COVID-19 pre-prints in 2020"
subtitle: "Markers of open code or data not found in 81 per cent of pre-prints"
author: 
  - Annie Collins^[University of Toronto.]
thanks: "Collins thanks CANSSI Ontario for financial support. Code and data are available at: https://github.com/anniecollins/reproducibility."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "We create a dataset of all the pre-prints published on arXiv and medRxiv between 28 January 2020 and 31 January 2021. We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print. We are unable to find markers of either open data or open code for 81 per cent of the pre-prints on medRxiv  in our sample, and X per cent of those on arXiv in our sample. Our paper demonstrates the need to have authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

@@

both <- rbind(just_arxiv, just_medRxiv)

both %>% 
  mutate(month = floor_date(date, "month")) %>% 
  filter(year(date) >= 2020) %>% 
  ggplot(aes(x = month)) + 
  geom_histogram(aes(fill = type), stat="count", position = "dodge") + 
  labs(title = "Pre-prints posted per month",
       subtitle = "Total of 3,379 relevant pre-prints on arXiv and 9,929 on medRxiv",
       x = "Month",
       y = "Number of pre-prints",
       fill = "Repository") +
  theme_minimal() +
  scale_fill_manual(values = wes_palette("Darjeeling1"))
```

@@

Broadly, we are unable to find markers of either open data or open code for around 81 per cent of the 1,200 sampled pre-prints. The remaining 19 per cent of pre-prints was comprised of 4 per cent of the sample containing markers for open code, 8 per cent of the sample with markers for open data, and 7 per cent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts)).

```{r summarycounts}
# open data/open code count summary table
med_open_data_results %>% 
  count(is_open_data, is_open_code) %>%
  mutate(prop_total = n / sum(n)) %>%
  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
        caption = "Counts and proportions of open data and code markers in our sample",
        booktabs = TRUE,
        digits = 2)
```

>>>>

---
title: "Reproducibility of COVID-19 pre-prints in 2020"
subtitle: "Markers of open code or data not found in 81 per cent of pre-prints"
author: 
  - Annie Collins^[University of Toronto.]
thanks: "Collins thanks CANSSI Ontario for financial support. Code and data are available at: https://github.com/anniecollins/reproducibility."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "We create a dataset of all the pre-prints published on arXiv, bioRxiv, and medRxiv between 28 January 2020 and 31 January 2021. We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print. We are unable to find markers of either open data or open code for 81 per cent of the pre-prints on medRxiv  in our sample, and X per cent of those on arXiv in our sample. Our paper demonstrates the need to have authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

bio_open_data_results <- 
  read_csv(here::here("outputs/data/bio_open_data_results.csv"))
bio_results <- 
  read_csv(here::here("outputs/data/bio_results.csv")) # All COVID bioRxiv papers (3,031)

@@

just_bioRxiv <- 
  bio_results  %>% 
  select(date) %>% 
  mutate(type = "bioRxiv")

all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv)

all %>% 
  mutate(month = floor_date(date, "month")) %>% 
  filter(year(date) >= 2020) %>% 
  ggplot(aes(x = month)) + 
  geom_histogram(aes(fill = type), stat="count", position = "dodge") + 
  labs(title = "Pre-prints posted per month",
       subtitle = "Total of 3,379 relevant pre-prints on arXiv, 3,031 on bioRxiv, 9,929 on medRxiv",
       x = "Month",
       y = "Number of pre-prints",
       fill = "Repository") +
  theme_minimal() +
  scale_fill_manual(values = wes_palette("Darjeeling1"))
```

@@

Broadly, we are unable to find markers of either open data or open code for around 81 per cent of the 1,200 sampled pre-prints. The remaining 19 per cent of pre-prints was comprised of 4 per cent of the sample containing markers for open code, 8 per cent of the sample with markers for open data, and 7 per cent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts-medRxiv)).

```{r summarycounts-medRxiv}
# open data/open code count summary table
med_open_data_results %>% 
  count(is_open_data, is_open_code) %>%
  mutate(prop_total = n / sum(n)) %>%
  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
        caption = "Counts and proportions of open data and code markers in medRxiv sample",
        booktabs = TRUE,
        digits = 2)
```

```{r summarycounts-bioRxiv}
# open data/open code count summary table
bio_open_data_results %>% 
  count(is_open_data, is_open_code) %>%
  mutate(prop_total = n / sum(n)) %>%
  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
        caption = "Counts and proportions of open data and code markers in bioRxiv sample",
        booktabs = TRUE,
        digits = 2)
```
